### 2017-02-26 Lab_3/solutions/L3-1-4.tex
Added Lab3 answers and questions file
Former-commit-id: 46eacfcfc8e8444bb6fd165479eac20335ab3f98

udp is hoger : minder overhead, gn congestion control dus resultaten zijn als verwacht
throughput stijgt omdat de bitrate ook omhoog gaat

usage verlaagt: sneller sturen -> meer retransmits en minder usage

>>>>

\includegraphics[width=0.5\textwidth]{traces/L3-1-4-tput.pdf}
\includegraphics[width=0.5\textwidth]{traces/L3-1-4-usage.pdf}
UDP's throughput is consistenly higher than TCP's. TCP has larger headers so more overhead. More importantly, TCP's congestion control mechanisms lead to reduced throughput. Throughput grows together with bitrate: the network supports sending more bits per second with higher bitrates. \\ \\
The throughput does not grow as quickly as the bitrate: with higher bitrates the bits are sent faster and bits are more likely to get lost. Due to this additional loss doubling the bitrate does not double the observed throughput. This translates to a decreasing usage with increasing bitrate.

### 2017-02-26 Lab_3/solutions/L3-3-1.tex
Added Lab3 answers and questions file
Former-commit-id: 46eacfcfc8e8444bb6fd165479eac20335ab3f98

The resulting udp and tcp streams (with rts/cts) have a throughput that is consistently lower than their non-rts/cts counterparts. Adding the rts/cts mechanism does not really help because the theoretical datarate is hard to achieve under normal circumstances.

in this case it is no different and we see that the added overhead of rts/cts slows down the realised throughput of the stream even more.

>>>>

\includegraphics[width=0.5\textwidth]{traces/L3-3-1-tput.pdf}
\includegraphics[width=0.5\textwidth]{traces/L3-3-1-usage.pdf}

For both TCP and UDP throughput is consistently lower with RTS/CTS enabled. The only communication in our tests is direct traffic between STA1 and AP (only STA1 $\rightarrow$ AP in case of UDP). There were few collisions even without RTS/CTS. This means RTS/CTS mainly adds overhead, leading to lower throughput. \\ \\ Even with RTS/CTS enabled UDP still outperforms TCP: TCP's lower performance is caused by its additional overhead and congestion control, which is not changed by having RTS/CTS enabled.
